---
title: "Sunlight analysis"
author: "Nanna Høgsholt"
date: "2021"
output: html_document
---

#This markdown contains a full analysis for BA thesis: 
 
 You will be able to find:
 - loading and pre-adjusting of data
 - Visual explorations and variable checks
 - Spatial explorations of x and y
 - Velocity analysis
 - Patterns within individual pairs 


#Loading data
```{r}
pacman::p_load(tidyverse, dplyr, pastecs, ggpmisc, lme4, viridis, ggsci, rstatix, extrafont)

#Base data
load(file = "C:/Users/nanna/Aarhus Universitet/Cordula Vesper - Sunlight material for Nanna/data/preprocessing/trapholt_preprocessing_nanna.rda")

#Merging interview data
df <- merge(d,trap)


#Loading stroke information
load(file="C:/Users/nanna/Aarhus Universitet/Cordula Vesper - Sunlight material for Nanna/condition_check/trapholt_condition_check_nanna.rda")

#Merging stroke information
df <- merge(df,test)

#Cleaning variables
df <- df %>% mutate_if(is.character,as.factor)

```



#Participant info
```{r}
summary(trap$age)
summary(trap$gender)
summary(as.factor(trap$used_hand))
summary(trap$dance_experience)
summary(trap$know_each_other)
```



#Exploring movement on x

```{r}
#For the whole experiment!
summary(df$x) #mean = -0.032 
sd(df$x) #sd = 0.25

#Checking distribution
ggplot(df, aes(x=x)) + 
  geom_histogram(aes(y=..density..),
                 binwidth = 0.05, 
                 fill="white",colour="black" ) + 
  stat_function(fun = dnorm, 
                args = list(mean = mean(df$x, na.rm= TRUE), 
                                         sd = sd(df$x, na.rm = TRUE)), 
                colour= "red", size = 1) + ggtitle("Distribution of x") 

#?sampledf?
qplot(sample=df$x) + xlab("Expected value") + ylab("Observed v
alue") + stat_qq()+stat_qq_line(colour='red')

#Testing normality with Anderson-Darling normality test
pacman::p_load(nortest)
ad.test(df$x)

#is normally distributed

#rescaling for plotting
df <- df %>%
  mutate(
    x_1 = (x*-1)
  )

#Mean of x in each part
ggplot(df, aes(x=part, y=x_1, fill = part)) + 
  geom_bar(stat='summary', fun.y=mean) + 
  geom_errorbar(stat='summary', fun.data=mean_se, width=0.5) + 
  scale_fill_startrek() + 
  theme_classic()
#looks interesting, we should rescale the data to make better sense of it. Seems like part 3 stays more towards the middle and part 2 is lower on the canvas. 

#Linear model of x
ggplot(df, aes(x=t, y=x_1, color = part)) + 
  geom_smooth(method = lm) + 
  scale_color_startrek() + 
  theme_classic() 
#part 2 is very steady about staying in the same x position, wheras part 1 and 3 seem to move downwards.

```

```{r}
#linear model on x to compare mean across parts

xmod <- lm(x~part, data=df)
summary(xmod)
#shows high significance between all parts
```
We want to explore the difference between the 3 parts of the experience

So we subset the 3 parts 
- P1: Free drawing 
- P2: Draw/move together 
- P3: Free drawing

```{r}
d_1 <- df %>%
  filter(part=="1")
d_2 <- df %>%
  filter(part=="2")
d_3 <- df %>%
  filter(part=="3")
```


Visualizing movement on the x axis for each part
```{r}
#part 1
ggplot(d_1, aes(t,x, color = subj)) + 
  geom_line() +
  facet_wrap(~pair) + 
  ggtitle("part 1 - free drawing")  

#part 2
ggplot(d_2, aes(t,x, color = subj)) + 
  geom_line() +
  facet_wrap(~pair) + 
  ggtitle("part 2 - draw /move together")

#part 3
ggplot(d_3, aes(t,x, color = subj)) + 
  geom_line() +
  facet_wrap(~pair) + 
  ggtitle("part 3 - free drawing") 

#some synchronizing is already visible here. There is a difference from part 1 to part 2. See fx part 12 or 17, 19, 22, 31. 

```

How far does the participants move on the canvas?

Range of x
```{r}

range(d_1$x) #-0.7972223  0.8833334 #seems to reach the limit of the canvas?
range(d_2$x) #-0.7986111  0.8833334
range(d_3$x) #-0.7986111  0.8486112

```

Comparing range of x
```{r}
#Finding Minimum position in x for each participant
d_minx <- df %>% 
    group_by(subj) %>% 
    slice(which.min(x))

#Renaming x to xMin
d_minx <- d_minx %>%
  rename(
    "xMin" =x
  )

#Finding Maximum position in x for each participant
d_maxx <- df %>% 
    group_by(subj) %>% 
    slice(which.max(x))

d_maxx <- d_maxx %>%
  rename(
    "xMax" =x
  )

#Merging dataframes
d_xrange <- merge(data.frame(d_maxx),data.frame(d_minx), by = "subj")

#Calculating range
d_xrange <- d_xrange %>%
  mutate(
    xrange = xMax-xMin
  )


xranmod <- lm(xrange ~ part.x, data = d_xrange)
summary(xranmod)


ggplot(d_xrange, aes(part.x,xrange, fill=part.x)) + 
  geom_bar(stat='summary', fun.y=mean) + 
  geom_errorbar(stat='summary', fun.data=mean_se, width=0.5) +  
  ggtitle("Range of x in each part")  + 
  scale_fill_startrek() + 
  theme_classic()

#No significant effect on range of x between parts

xranmodcond <- lm(xrange ~ cond_label.x, data = d_xrange)
summary(xranmodcond)
confint(xranmodcond, oldNames = FALSE)

ggplot(d_xrange, aes(cond_label.x,xrange, fill=cond_label.x)) + 
  geom_bar(stat='summary', fun.y=mean) + 
  geom_errorbar(stat='summary', fun.data=mean_se, width=0.5) + 
  ggtitle("A) Range of x in each condition")  + 
  scale_fill_futurama(name="Condition") + 
  theme_classic() + 
  theme(axis.title.x = element_blank(),
        axis.text.x=element_blank())


```

##Exploring y
```{r}
#For the whole experiment!
summary(df$y) #mean = 0.068
sd(df$y) #sd =0.12

#Checking distribution
ggplot(df, aes(x=y)) + 
  geom_histogram(aes(y=..density..),
                 binwidth = 0.05, fill="white",c
                 olour="black" ) +
  stat_function(fun = dnorm, 
                args = list(mean = mean(df$x, na.rm= TRUE), 
                            sd = sd(df$x, na.rm = TRUE)), 
                colour= "red", size = 1) + 
  ggtitle("Distribution of y") 
#normally distributed, but a bit skewed!

#?sampledf?
qplot(sample=df$y) + xlab("Expected value") + ylab("Observed v
alue") + stat_qq()+stat_qq_line(colour='red')

#Testing normality with Anderson-Darling normality test
#pacman::p_load(nortest)
ad.test(df$y) 

#seems to be okay

#Mean of y in each part
ggplot(df, aes(x=part, y=y, fill = part)) + 
  geom_bar(stat='summary', fun.y=mean) + 
  geom_errorbar(stat='summary', fun.data=mean_se, width=0.5) + 
  scale_fill_startrek() + 
  theme_classic()
#higher mean in part 2

#Linear model of y
ggplot(df, aes(x=t, y=y, color = part)) + 
  geom_smooth(method = lm) + 
  scale_color_startrek() + 
  theme_classic() 
#part 2 is very steady about staying in the same x position, wheras part 1 and 3 seem to move downwards.

```

```{r}
#linear model on y to compare mean across parts

ymod <- lm(y~part, data=df)
summary(ymod)
#shows high significance between all parts
```


Visualizing movement on the y axis for each part
```{r}
#part 1
ggplot(d_1, aes(t,y, color = subj)) + 
  geom_line() +
  facet_wrap(~pair) + 
  ggtitle("part 1 - free drawing")

#part 2
ggplot(d_2, aes(t,y, color = subj)) + 
  geom_line() +
  facet_wrap(~pair) + 
  ggtitle("part 2 - draw /move together")

#part 3
ggplot(d_3, aes(t,y, color = subj)) + 
  geom_line() +
  facet_wrap(~pair) + 
  ggtitle("part 3 - free drawing")


#This is a bit more messy, but some synchronisation is also visible here
```

Range of y
```{r}

range(d_1$y) #-0.3583333  0.3986111
range(d_2$y) #-0.3513889  0.3986111
range(d_3$y) #-0.3291667  0.3986111

```

Comparing range of y
```{r}
#Finding Minimum position in x for each participant
d_miny <- df %>% 
    group_by(subj) %>% 
    slice(which.min(y))

#Renaming y to xMin
d_miny <- d_miny %>%
  rename(
    "yMin" =y
  )

#Finding Maximum position in y for each participant
d_maxy <- df %>% 
    group_by(subj) %>% 
    slice(which.max(y))

d_maxy <- d_maxy %>%
  rename(
    "yMax" =y
  )

#Merging dataframes
d_yrange <- merge(data.frame(d_maxy),data.frame(d_miny), by = "subj")

#Calculating range
d_yrange <- d_yrange %>%
  mutate(
    yrange = yMax-yMin
  )


yranmod <- lm(yrange ~ part.y, data = d_yrange)
summary(yranmod)


ggplot(d_yrange, aes(part.y,yrange, fill=part.y)) + 
  geom_bar(stat='summary', fun.y=mean) + 
  geom_errorbar(stat='summary', fun.data=mean_se, width=0.5) +  
  ggtitle("Range of y in each part")  + 
  scale_fill_startrek() + 
  theme_classic()

#No significant effect on range of y between parts

yranmodcond <- lm(yrange ~ cond_label.y, data = d_yrange)
summary(xranmodcond)
confint(yranmodcond, oldNames = FALSE)



ggplot(d_yrange, aes(cond_label.y,yrange, fill=cond_label.y)) +
  geom_bar(stat='summary', fun.y=mean) + 
  geom_errorbar(stat='summary', fun.data=mean_se, width=0.5) + 
  ggtitle("b) Range of y in each Condition")  + 
  scale_fill_futurama(name = "Conditon") + 
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.text.x=element_blank())
  

```


#Heatmapping
```{r}
#Parts        
ggplot(df, aes(x=y, y=x)) +
  stat_density_2d(aes(fill = ..level..), geom = "polygon") + 
  facet_wrap(~part) + 
  ggtitle("A) Movement across all 3 parts") + 
  scale_fill_viridis_c(option = "plasma") + 
  theme_minimal()

#Conditions
ggplot(df2, aes(x=y, y=x)) +
  stat_density_2d(aes(fill = ..level..), geom = "polygon") +
  facet_wrap(~cond_label) + 
  ggtitle("B) Movement across conditions") + 
  scale_fill_viridis_c(option = "plasma") +
  theme_minimal()

```

#Distance in space between individual pairs

```{r}
#Creating a wide dataframe
  #selecting only relevant variables
dfwide <- df %>%
  select(
    pair,
    cond_label,
    subj,
    part,
    t,
    x,
    y,
    v
  )

#Finding participant 1 and 2
dfwide <- dfwide %>%
  mutate(
    subjnum = str_replace(subj, "\\d{3}", "")
  )

dfwide <- dfwide %>%
  mutate(
    subjnum = as.factor(subjnum)
  )

dfwide <- dfwide %>%
  select(-subj)


#pivoting data so we get two columns for each variable for subject 1 and subject 2 separately
dfwide <- dfwide %>%
  pivot_wider(names_from = subjnum, values_from = c(x,y,v))


```

#Calculating differences on the two axes

Parts
```{r}
#calculating difference in space between subject 1 and 2
dfwide <- dfwide%>%
  mutate(
    x_dif = x_1-x_2,
    y_dif = y_1-y_2
  )

#absolute numbers
dfwide <- dfwide%>%
  mutate(
    x_dif_abs = abs(x_dif),
    y_dif_abs = abs(y_dif)
  )

#Difference in part for x
ggplot(dfwide, aes(x=part, y= x_dif_abs, fill = part)) + 
  geom_bar(stat='summary', fun.y=mean) + 
  geom_errorbar(stat='summary', fun.data=mean_se, width=0.5) + 
  scale_fill_futurama() + 
  theme_minimal() + 
  ggtitle("Difference in x between subjects in parts") + 
  ylim(0,0.3)

x_dif_mod <- lm(x_dif_abs ~ part, data = dfwide)
summary(x_dif_mod)

#Difference in part for y
ggplot(dfwide, aes(x=part, y= y_dif_abs, fill = part)) + 
  geom_bar(stat='summary', fun.y=mean) + 
  geom_errorbar(stat='summary', fun.data=mean_se, width=0.5) + 
  scale_fill_futurama() + 
  theme_minimal() + 
  ggtitle("Difference in y between subjects in parts") + 
  ylim(0,0.3)

y_dif_mod <- lm(y_dif_abs ~ part, data = dfwide)
summary(y_dif_mod)


```


Conditions
```{r}
#Seperetaing df wide with only part 2 data

dfwide2 <- dfwide %>%
  filter(
    part =="2")


#Difference in condition for x
ggplot(dfwide2, aes(x=cond_label, y= x_dif_abs, fill = cond_label)) + 
  geom_bar(stat='summary', fun.y=mean) + 
  geom_errorbar(stat='summary', fun.data=mean_se, width=0.5) + 
  scale_fill_futurama() + 
  theme_minimal() + 
  ggtitle("Difference in x between subjects in conditions") + 
  ylim(0,0.3)

x_dif_cond_mod <- lm(x_dif_abs ~ cond_label, data = dfwide2)
summary(x_dif_cond_mod)

#Difference in condition for y
ggplot(dfwide2, aes(x=cond_label, y= y_dif_abs, fill = cond_label)) + 
  geom_bar(stat='summary', fun.y=mean) + 
  geom_errorbar(stat='summary', fun.data=mean_se, width=0.5) + 
  scale_fill_futurama() + 
  theme_minimal() + 
  ggtitle("Difference in y between subjects in conditions") + 
  ylim(0,0.3)


y_dif_cond_mod <- lm(y_dif_abs ~ cond_label, data = dfwide2)
summary(x_dif_mod)

```


#Absolute distance in space between participants 
```{r}
#calculating distance
dfwide <- dfwide %>%
  mutate(
    dist = abs(sqrt(((x_2-x_1)^2) - ((y_2-y_1)^2)))
    )

#Checking distribution
ggplot(dfwide, aes(x=dist)) + 
  geom_histogram(aes(y=..density..),
                 binwidth = 0.05, 
                 fill="white",
                 colour="black" ) + 
  stat_function(fun = dnorm, 
                args = list(mean = mean(dfwide$dist, na.rm= TRUE), 
                                         sd = sd(dfwide$dist, na.rm = TRUE)), 
                colour= "#E69F00", size = 1) + 
  theme_minimal() + 
  ggtitle("Distribution of distance")

#plotting quantiles 
qplot(sample=dfwide$dist) + xlab("Expected value") + ylab("Observed value") + stat_qq()+stat_qq_line(colour="#E69F00") + theme_minimal()

#Testing normality with Anderson-Darling normality test
#pacman::p_load(nortest)
ad.test(dfwide$dist)
#Not normal, so we transform with sqrt

dfwide <- dfwide %>%
  mutate(
    dist_sqrt = sqrt(dist)
  )


ggplot(dfwide, aes(x=dist_sqrt)) + 
  geom_histogram(aes(y=..density..),
                 binwidth = 0.05, 
                 fill="white",
                 colour="black" ) + 
  stat_function(fun = dnorm, 
                args = list(mean = mean(dfwide$dist_sqrt, na.rm= TRUE), 
                                         sd = sd(dfwide$dist_sqrt, na.rm = TRUE)), 
                colour= "#E69F00", size = 1) + 
  theme_minimal() + 
  ggtitle("Distribution of distance")
```


Modelling
```{r}
dfwide %>%
  group_by(part) %>%
  get_summary_stats(dist, type = "mean_sd")


distmpart1 <- lmerTest::lmer(dist_sqrt~part*cond_label + (1|pair), data = dfwide)
summary(distmpart1)
anova(distmpart1)
plot(distmpart1)
qqnorm(resid(distmpart1))
confint(distmpart1, oldNames = FALSE)

#R squared
MuMIn::r.squaredGLMM(distmpart1)

ggplot(dfwide, aes(part, dist, fill=part)) +
  geom_bar(stat='summary', fun.y=mean) + 
  geom_errorbar(stat='summary', fun.data=mean_se, width=0.5)+ 
  facet_wrap(~cond_label)+
  ggtitle("Absolute distance between individual pairs") + 
  scale_fill_futurama() + 
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x=element_blank())

```



##Explore v
```{r}
```{r}
#Checking distribution
ggplot(df, aes(x=v)) + 
  geom_histogram(aes(y=..density..),
                 binwidth = 0.0002, 
                 fill="white",
                 colour="black" ) + 
  stat_function(fun = dnorm, 
                args = list(mean = mean(df$v, na.rm= TRUE), 
                                         sd = sd(df$v, na.rm = TRUE)), 
                colour= "#E69F00", size = 1) + 
  theme_minimal() + 
  ggtitle("Distribution of v") 

#not normally distributed

#plotting quantiles 
qplot(sample=df$v) + xlab("Expected value") + ylab("Observed value") + stat_qq()+stat_qq_line(colour="#E69F00") + theme_minimal()

#Testing normality with Anderson-Darling normality test
#pacman::p_load(nortest)
ad.test(df$v)

#significant departure from normality was found 

#logtransforming v

df <- df %>%
  mutate(
    v_log = log(v),
    v_sqrt = sqrt(v)
  )
#log hist
ggplot(df, aes(x=v_log)) + 
  geom_histogram(aes(y=..density..),
                 binwidth = 0.0002, 
                 fill="white",
                 colour="black" ) + 
  stat_function(fun = dnorm, 
                args = list(mean = mean(df$v_log, na.rm= TRUE), 
                                         sd = sd(df$v_log, na.rm = TRUE)), 
                colour= "#E69F00", size = 1) + 
  theme_minimal() + 
  ggtitle("Distribution of v log")

#sqrt hist
ggplot(df, aes(x=v_sqrt)) + 
  geom_histogram(aes(y=..density..),
                 binwidth = 0.0002, 
                 fill="white",
                 colour="black" ) + 
  stat_function(fun = dnorm, 
                args = list(mean = mean(df$v_sqrt, na.rm= TRUE), 
                                         sd = sd(df$v_sqrt, na.rm = TRUE)), 
                colour= "#E69F00", size = 1) + 
  theme_minimal() + 
  ggtitle("Distribution of v sqrt")

#plotting quantiles 
qplot(sample=df$v_sqrt) + xlab("Expected value") + ylab("Observed value") + stat_qq()+stat_qq_line(colour="#E69F00") + theme_minimal()

#Testing normality with Anderson-Darling normality test
#pacman::p_load(nortest)
ad.test(df$v_sqrt)


#log did not fix but sqrt did transform v to a normal distribution

```



Modeling
```{r}

vm1_2 <- lmerTest::lmer(v_sqrt ~ t*part*cond_label +(1|pair), data = df)
summary(vm1_2)
anova(vm1_2)
MuMIn::r.squaredGLMM(vm1_2)
confint(vm1_2, oldNames = FALSE)
plot(vm1_2)
qqnorm(residuals(vm1_2))

difflsmeans(vm1_2)
Anova(vm1_2)



ggplot(df, aes(x=t, y=v, color = part)) + 
  geom_smooth(method = lm) +
  facet_wrap(~cond_label) +
  ggtitle("Absolute distance between pairs through time")+
  scale_color_futurama() + 
  theme_minimal()


ggplot(df, aes(cond_label, v, fill=cond_label)) +
  geom_bar(stat='summary', fun.y=mean) + 
  geom_errorbar(stat='summary', fun.data=mean_se, width=0.5)+ 
  scale_fill_futurama() + 
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x=element_blank())
```



#individual patterns

```{r}
df2 <- df %>%
  filter(part=="2")

#all movement on x
ggplot(df2, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  theme_minimal() +
  facet_wrap(~pair)

#pair 12 - move - >70 - m/f - right hand - long-term
pair12 <- df2 %>%
  filter(pair=="12")

ggplot(pair12, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()


ggplot(pair12, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

#part 2 by minutes
pair12_1 <- pair12 %>%
  filter(t < 60000)
pair12_2 <- pair12 %>%
  filter(t > 60000, t < 120000)
pair12_3 <- pair12 %>%
  filter(t > 120000)

ggplot(pair12_1, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair12_2, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair12_3, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

pair12_3_1 <- pair12 %>%
  filter(t > 110000, t < 115000)

ggplot(pair12_3_1, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair12_3_1, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()



```


```{r}
#pair 31 - draw - <20/40-49 - m/f - right hand - long-term
pair31 <- df2 %>%
  filter(pair=="31")

ggplot(pair31, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()


ggplot(pair31, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()


#part 2 by minutes
pair31_1 <- pair31 %>%
  filter(t < 60000)
pair31_2 <- pair31 %>%
  filter(t > 60000, t < 120000)
pair31_3 <- pair31 %>%
  filter(t > 120000)

ggplot(pair31_1, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair31_2, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair31_3, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair31_1, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair31_2, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair31_3, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

#Heatmap
ggplot(pair31_2, aes(x=y, y=x)) +
  stat_density_2d(aes(fill = ..level..), geom = "polygon") +
  facet_wrap(~subj) + 
  ggtitle("Pair 31") + 
  scale_fill_viridis_c(option = "plasma") +
  theme_minimal()

```


```{r}
#pair 19 - draw - 40-49 - m/f - both hands - never
pair19 <- df2 %>%
  filter(pair=="19")

ggplot(pair19, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()


ggplot(pair19, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()


#part 2 by minutes
pair19_1 <- pair19 %>%
  filter(t < 60000)
pair19_2 <- pair19 %>%
  filter(t > 60000, t < 120000)
pair19_3 <- pair19 %>%
  filter(t > 120000)

#x and y
ggplot(pair19_1, aes(x=y, y=x, color = subj)) + 
  geom_point() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair19_1, aes(x=y, y=x, color = t)) + 
  geom_point() + 
  scale_color_viridis_c(option = "plasma") + 
  theme_minimal() +
  facet_wrap(~subj)

#x and time
ggplot(pair19_1, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair19_2, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair19_3, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair19_1, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair19_2, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair19_3, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

```

```{r}
#pair 26
pair26 <- df2 %>%
  filter(pair=="26")

ggplot(pair26, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()


ggplot(pair26, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

#part 2 by minutes
pair26_1 <- pair26 %>%
  filter(t < 60000)
pair26_2 <- pair26 %>%
  filter(t > 60000, t < 120000)
pair26_3 <- pair26 %>%
  filter(t > 120000)

ggplot(pair26_1, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair26_2, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair26_3, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair26_1, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair26_2, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair26_3, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()
```

```{r}
#pair 14 
pair14 <- df2 %>%
  filter(pair=="14")

ggplot(pair14, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()


ggplot(pair14, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()


#part 2 by minutes
pair14_1 <- pair14 %>%
  filter(t < 60000)
pair14_2 <- pair14 %>%
  filter(t > 60000, t < 120000)
pair14_3 <- pair14 %>%
  filter(t > 120000)

ggplot(pair14_1, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair14_2, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair14_3, aes(x=t, y=x, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair14_1, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair14_2, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair14_3, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

pair14_1_1 <- pair14 %>%
  filter(t > 45000, t < 60000)

ggplot(pair14_1_1, aes(x=t, y=y, color = subj)) + 
  geom_line() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair14_1_1, aes(x=y, y=x, color = subj)) + 
  geom_point() + 
  scale_color_futurama() + 
  theme_minimal()

ggplot(pair14_1_1, aes(x=y, y=x, color = t)) + 
  geom_point() + 
  scale_color_viridis_c(option = "plasma") + 
  theme_minimal() +
  facet_wrap(~subj)

```




